% =====================================================================
% Appendix: Extended experimental details
% Required generated files:
%   docs/tables/v4/appendix_remaining_50_summary.tex
%   docs/tables/v4/appendix_remaining_50_r1r4.tex
%   docs/tables/v4/appendix_remaining_50_cost.tex
%   docs/tables/v4/appendix_prompt_bank.tex
% Optional generated manifests:
%   results/v4/artifact_manifest.json
%   results/v4_matrix/merged_manifest.json
% =====================================================================

\section{Extended experimental details}
\label{appendix:exp_details}

This appendix gives the implementation-level details behind Section~\ref{sec:experiments}. The
main text reports six headline model--dataset cells selected for scale and task diversity; here we
describe the full \(7\times 8\) matrix, the local/remote execution split, the artifact pipeline, the
baseline implementation, and the prompt templates used by the end-to-end benchmark. The generated
tables in this appendix are produced by \texttt{scripts/v4\_make\_latex\_tables.py} from the same
v4 metric schema used to build the figures.

\subsection{Matrix construction and cell selection}
\label{appendix:exp_details:matrix}

The full benchmark contains seven LLM backends and eight datasets, yielding \(56\) model--dataset
cells. We split the matrix into a \(5\times 8\) local block and a \(2\times 8\) remote block. The
local block uses \texttt{phi-3.5-mini}, \texttt{qwen2.5-7B},
\texttt{deepseek-llm-7b-chat}, \texttt{Llama-3.1-8B}, and
\texttt{Gemma-2-9b-it}. The remote block uses \texttt{Llama-3.3-70B} and
\texttt{deepseek-v3}, because these runs require gated model access, larger memory, quantization,
or a hosted inference endpoint. The main-text six-cell subset was chosen before analysis to span
model scale and task type: fact verification, multi-hop QA, biomedical QA, table--text finance,
tool use, and web interaction. The remaining 50 cells are reported below.

\input{.../appendix_remaining_50_summary}

\subsection{Execution layout and reproducibility contract}
\label{appendix:exp_details:execution}

The repository separates raw experiment execution from paper-facing artifact generation. Local
experiments are launched through \texttt{scripts/v4\_run\_matrix\_local.py}; remote experiments are
launched through \texttt{scripts/v4\_run\_matrix\_remote.py} or the generated Colab notebook
\texttt{notebooks/pcg\_v4\_colab\_16cells.ipynb}. To avoid accidental full-matrix launches, both
matrix runners require an explicit \texttt{--allow-full-run} flag for the complete matrix. Each cell
writes into a deterministic folder of the form
\[
\texttt{results/v4\_matrix/\{local,remote\}/<dataset>\_\_<model>/},
\]
with one completion marker per experiment family. Remote results are copied back from Colab or the
HF inference environment and reconciled by \texttt{scripts/v4\_reconcile\_remote\_results.py}, which
writes \texttt{results/v4\_matrix/merged\_manifest.json}. Paper-facing artifacts are collected by
\texttt{scripts/v4\_collect\_artifacts.py}, which writes \texttt{results/v4/artifact\_manifest.json}.

The intended execution sequence is:
\[
\begin{array}{l}
\texttt{v4\_make\_proxy\_metrics.py}
\rightarrow
\texttt{intro\_hero\_v4.py}
\rightarrow
\texttt{v4\_make\_r1\_r5\_figures.py}
\rightarrow
\texttt{v4\_make\_latex\_tables.py}
\rightarrow
\texttt{v4\_reconcile\_remote\_results.py}
\rightarrow
\texttt{v4\_collect\_artifacts.py}.
\end{array}
\]
The same build order is wrapped by \texttt{scripts/v4\_build\_paper\_artifacts.py}. This separation is
intentional: the expensive model-generation layer can be run locally or remotely, while the
figure/table layer can be regenerated quickly from a consolidated metric manifest.

\subsection{Baselines and method variants}
\label{appendix:exp_details:baselines}

We compare three operating modes. \texttt{No certificate} accepts the agent output without a
replayable evidence/execution certificate. It therefore measures the default risk of the underlying
agentic generation stack. \texttt{SHIELDAGENT} is implemented as a policy-reasoning guardrail
baseline: it reads the action trajectory and policy context, checks safety-policy consistency, and
emits a safety label or explanation. It captures a strong recent direction in trajectory-level
safety shielding, but it does not require committed evidence hashes, replayable support pipelines,
independent support paths, or replay-interventional responsibility. \texttt{PCG-MAS} uses the full
certificate contract: evidence commitments, replay, deterministic checking, redundancy, diagnosis,
and risk-aware control. This makes \texttt{PCG-MAS} more expensive than a policy-only guardrail, but
also gives a stronger audit object.

\subsection{R1--R4 diagnostic complement over the remaining cells}
\label{appendix:exp_details:r1r4}

Table~\ref{tab:appendix_remaining_50_r1r4} complements
Table~\ref{tab:r1_r4_combined}. It reports the same diagnostic quantities for the 50 cells not shown
in the main text. \(\mathrm{Audit\ cov.}\) measures how much of the observed bad-accept behavior is
explained by the four auditable failure channels. \(\mathrm{Safety\ gain}\) is the multiplicative
harm reduction from \texttt{No certificate} to \texttt{PCG-MAS}. \(\mathrm{Resp.\ lift}\) is the
percentage-point improvement of replay responsibility over the policy-shielding baseline.
\(\mathrm{Control\ gain}\) is the harm-weighted operating-cost gain achieved by certificate-derived
risk control.

\input{.../appendix_remaining_50_r1r4}

\subsection{Overhead complement over the remaining cells}
\label{appendix:exp_details:overhead}

Table~\ref{tab:appendix_remaining_50_cost} complements Table~\ref{tab:cost_overhead_main}. The
reported values are token multipliers relative to the no-certificate pipeline. The ordering is
deliberate: \texttt{No certificate} is cheapest, \texttt{SHIELDAGENT} adds moderate policy-reasoning
cost, and \texttt{PCG-MAS} adds the largest overhead because it constructs certificates, checks
replay, enforces redundancy, and supports mask-and-replay diagnosis. We view this as an explicit
safety--cost trade-off rather than a hidden cost: the main claim is not that \texttt{PCG-MAS} is the
cheapest method, but that the additional overhead buys externally checkable groundedness and
diagnosability.

\input{.../appendix_remaining_50_cost}

\subsection{Prompt and tool-call templates}
\label{appendix:exp_details:prompts}

Table~\ref{tab:appendix_prompt_bank} reports the prompt and tool-call templates used across the
benchmark. The table is generated by \texttt{scripts/v4\_make\_latex\_tables.py} and is designed to
make the experimental harness inspectable from a software-engineering perspective. The prompt bank
covers candidate generation, certificate construction, unified checking, SHIELDAGENT-style policy
shielding, redundancy selection, audit probing, mask-and-replay responsibility, risk control, and
remote-result reconciliation. This table is intentionally broad because PCG-MAS is not a single
prompting trick: it is an execution contract spanning generation, verification, logging, replay,
diagnosis, and control.

\input{.../appendix_prompt_bank}

\subsection{Artifact generation and file-level reproducibility}
\label{appendix:exp_details:artifacts}

All paper-facing figures and tables are generated from repository scripts rather than manually
edited. The introduction figure is produced by \texttt{src/pcg/eval/intro\_hero\_v4.py}; the R1--R5
figures are produced by \texttt{scripts/v4\_make\_r1\_r5\_figures.py}; and the tables in
Section~\ref{sec:experiments} and this appendix are produced by
\texttt{scripts/v4\_make\_latex\_tables.py}. The artifact collector records the generated figures,
tables, metric files, local matrix outputs, remote matrix outputs, and completion markers in
\texttt{results/v4/artifact\_manifest.json}. This manifest is used only for reproducibility and
software sanity checks; the manuscript imports the generated \texttt{.pdf} figures and
\texttt{.tex} tables directly.

\subsection{Interpreting proxy, smoke, and full-matrix modes}
\label{appendix:exp_details:modes}

The repository supports two execution modes. In \emph{smoke/artifact mode}, deterministic metric
files are generated quickly to verify the end-to-end figure/table pipeline, stress-test layout, and
ensure that the code paths for \texttt{No certificate}, \texttt{SHIELDAGENT}, and \texttt{PCG-MAS}
are consistently represented. In \emph{full-matrix mode}, the local \(5\times8\) block and remote
\(2\times8\) block are executed over the requested seeds and example counts, then reconciled into the
same metric schema. This design ensures that replacing smoke metrics with full-run metrics does not
require changing the LaTeX, plotting scripts, or table-generation scripts. Only the consolidated
metric manifest changes.

\subsection{Why these diagnostics are necessary}
\label{appendix:exp_details:diagnostic_rationale}

The five experiment families test complementary aspects of the certificate contract. R1 asks whether
failures are externally auditable rather than merely observed. R2 asks whether independent support
paths reduce false acceptance under controlled adversarial stress. R3 asks whether a failure can be
localized to a runtime component after acceptance. R4 asks whether certificate risk is useful as a
decision signal for \texttt{Answer}, \texttt{Verify}, \texttt{Escalate}, and \texttt{Refuse}. R5
asks whether the cost of the contract is measurable and bounded. This is the central empirical
reason for benchmarking against both \texttt{No certificate} and \texttt{SHIELDAGENT}: the former
tests the value of verification itself, while the latter tests whether full proof-carrying replay and
diagnosis add value beyond policy-level trajectory shielding.


%%%%%%%%%%%%%%%%%%%%%%
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
%%%%%%%%%%%%%%%%%%%%